Stateless Model Checking with Data-Race Preemption Points

### 2016-07-20 oopsla-16/evaluation.tex
garth revisions
don't hyphenate Limited-HB (unless QS-Limited-HB)

	\item Does \quicksand~improve upon state-of-the-art MC?
		\begin{enumerate}
			\revision{\item} Do data-race PPs expose new bugs that couldn't be found with SSS-MC's fixed-PP-set approach?
				% Elaborate later:
				% Among those, how many were missed in a {\em completed} execution of the otherwise ``maximal'' state space?
			\revision{\item} Does \quicksand~find bugs faster
				%than SSS-MC
				in subset state spaces, even without data-race PPs?
			% Probably not... ICB is state of the art here.
			% In large tests, can Iterative Deepening provide partial verification by completing smaller state spaces
			\revision{
			\item Does \quicksand~provide more full verifications of bug-free programs more quickly?
			}
			\revisionx{
			\item How does the choice between HB and Limited-HB affect bug-finding and verification performance?
			}
		\end{enumerate}
	\item Does MC improve the accuracy of data-race detection?
		\begin{enumerate}
		\item Does \quicksand~avoid false positives compared to a single-execution \revisionx{Limited-HB} data race analysis?
				% Explain later as:
				% How many data-race candidates were verified as benign
				% But to be fair, you have to count how many DRs are reported as "couldn't test these, check yourself" at the end.
				% Also Include:
				% How many false positives does the free-re-malloc technique suppress?
				% to do (done) If you have time, re-run all of the dr-only bug tests, with DR_FALSE_NEG enabled, and see how much fewer bugs get found (how many bugs get pushed past the time limit?)
				% Answer: Just 1. (for p2s at least; as of time of writing, pintos dr-falsenegs not run yet)
			\item Does \quicksand~find data-race bugs that would be false-negatives during a single-execution analysis?%Do we avoid false negatives compared to single-pass?
		\end{enumerate}
\end{enumerate}

@@

To evaluate the benefits of data-race PPs and Iterative Deepening separately, we ran the test suite under \quicksand~in \revisionx{three} different configurations, each of which was given a 1-hour budget and 10 CPUs for each test.
\begin{itemize}
		\revisionx{
	\item {\bf QS-Limited-HB}: \quicksand~using Limited-HB for its data-race analysis,
	\item {\bf QS-Pure-HB}: \quicksand~using pure HB instead, and
		}
	\item {\bf QS-Sync-Only}: \quicksand~with PPs still seeded as described in \sect{\ref{sec:initial-pp}}, but never adding new PPs from reported data-race candidates.
\end{itemize}

@@

\begin{figure}[t]
	\hspace{-1em}
		\revision{
	\begin{tabular}{p{0.48\textwidth}}
	\includegraphics[width=0.48\textwidth]{dowefindbugsfaster-v2.pdf} \\
		(a) Bugs found \revisionx{as a function of} elapsed CPU time. Overall,
		a more \revisionx{resource-fair} comparison than (b),
		although \quicksand's start-up overhead is exaggerated, as the SSS-MC tests are not parallelized. \\
		\\
	\includegraphics[width=0.48\textwidth]{dowefindbugsfaster-wallclock-v2.pdf} \\
		(b) Bugs found by elapsed wall-clock time.
		\quicksand~is parallelized tenfold; the vertical line indicates its 1 hour limit. \\
	\end{tabular}
	}
	\caption{Comparison of bug-finding performance
	by several configurations of \quicksand~and the SSS-MC control.
	\quicksand~finds \revisionx{125\%} as many bugs with data-race PPs.}
	\label{fig:dowefindbugsfaster}
\end{figure}

>>>>

	\item Does \quicksand~improve upon state-of-the-art MC?
		\begin{enumerate}
			\revision{\item} Do data-race PPs expose new bugs that couldn't be found with SSS-MC's fixed-PP-set approach?
				% Elaborate later:
				% Among those, how many were missed in a {\em completed} execution of the otherwise ``maximal'' state space?
			\revision{\item} Does \quicksand~find bugs faster
				%than SSS-MC
				in subset state spaces, even without data-race PPs?
			% Probably not... ICB is state of the art here.
			% In large tests, can Iterative Deepening provide partial verification by completing smaller state spaces
			\revision{
			\item Does \quicksand~provide more full verifications of bug-free programs more quickly?
			}
			\revisionx{
			\item How does the choice between HB and Limited HB affect bug-finding and verification performance?
			}
		\end{enumerate}
	\item Does MC improve the accuracy of data-race detection?
		\begin{enumerate}
		\item Does \quicksand~avoid false positives compared to a single-execution \revisionx{Limited HB} data race analysis?
				% Explain later as:
				% How many data-race candidates were verified as benign
				% But to be fair, you have to count how many DRs are reported as "couldn't test these, check yourself" at the end.
				% Also Include:
				% How many false positives does the free-re-malloc technique suppress?
				% to do (done) If you have time, re-run all of the dr-only bug tests, with DR_FALSE_NEG enabled, and see how much fewer bugs get found (how many bugs get pushed past the time limit?)
				% Answer: Just 1. (for p2s at least; as of time of writing, pintos dr-falsenegs not run yet)
			\item Does \quicksand~find data-race bugs that would be false-negatives during a single-execution analysis?%Do we avoid false negatives compared to single-pass?
		\end{enumerate}
\end{enumerate}

@@

To evaluate the benefits of data-race PPs and Iterative Deepening separately, we ran the test suite under \quicksand~in \revisionx{three} different configurations, each of which was given a 1-hour budget and 10 CPUs for each test.
\begin{itemize}
		\revisionx{
	\item {\bf QS-Limited-HB}: \quicksand~using Limited HB for its data-race analysis,
	\item {\bf QS-Pure-HB}: \quicksand~using pure HB instead, and
		}
	\item {\bf QS-Sync-Only}: \quicksand~with PPs still seeded as described in \sect{\ref{sec:initial-pp}}, but never adding new PPs from reported data-race candidates.
\end{itemize}

@@

\begin{figure}[t]
	\hspace{-1em}
		\revision{
	\begin{tabular}{p{0.48\textwidth}}
	\includegraphics[width=0.48\textwidth]{dowefindbugsfaster-v2.pdf} \\
		(a) Bugs found \revisionx{as a function of} elapsed CPU time. Overall,
		a more \revisionx{resource-fair} comparison than (b),
		although \quicksand's start-up overhead is exaggerated, as the SSS-MC tests are not parallelized. \\
		\\
	\includegraphics[width=0.48\textwidth]{dowefindbugsfaster-wallclock-v2.pdf} \\
		(b) Bugs found by elapsed wall-clock time.
		\quicksand~is parallelized tenfold; the vertical line indicates its 1 hour limit. \\
	\end{tabular}
	}
	\caption{Comparison of bug-finding performance
	by several configurations of \quicksand~and the SSS-MC control.
	\quicksand~finds \revisionx{125\%} as many bugs \revisionx{at the 10-hour mark compared to the best SSS-MC approach}.}
	%with data-race PPs.}
	\label{fig:dowefindbugsfaster}
\end{figure}
